Figure 5 - IP-MS

### 2024-08-05 ms_figure_5_ipms.Rmd
Add annotations Fig5

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, 
                    idmap = idmap),
                top_annotation = makeTFIntAnnotation(baitdata_150), 
                width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 2.2, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

set.seed(42L)
hm_150_bait <- grid.grabExpr(
    hm1b <- draw(hm1b, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm / 1.05, height = h_ipmsHm / 2.2
)

@@

dbd_colors <- c(`KilA-N` = main_colors[5], 
                `Zn(II)2Cys6` = main_colors[4],
                bZIP = main_colors[3], 
                `Other (combined)` = bg_color)
lgd_dbd <- Legend(labels = names(dbd_colors), 
                  legend_gp = gpar(fill = dbd_colors), 
                  title = "DBD family", nrow = 2)

@@

hm1b_loose <- Heatmap(baitdata_150_loose$mat, 
                      cluster_rows = FALSE, 
                      cluster_columns = FALSE, 
                      col = makeHeatmapCol(stringency = "low"), 
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.", 
                      na_col = binary_heatmap_colors["FALSE"],
                      column_title = paste(c("150 mM NaCl", rep(" ", 45)), collapse = ""),
                      row_title = "Transcription factors",
                      column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                      row_title_gp = gpar(fontsize = fl),
                      column_names_gp = gpar(fontsize = fs),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = FALSE, show_column_names = FALSE,
                      use_raster = FALSE, show_heatmap_legend = TRUE, 
                      left_annotation = makeComplexAndDBDAnnotation(
                          baitdata_150_loose$mat, 
                          complexes[c("MBF transcription complex", 
                                      "CCAAT-binding factor complex",
                                      "Atf1-Pcr1")],
                          dbd = dbd, 
                          idmap = idmap),
                      top_annotation = makeTFIntAnnotation(baitdata_150_loose), 
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                      heatmap_height = unit(h_ipmsHm / 2.2, "mm"), 
                      heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                                  border = "gray10",
                                                  border_gp = gpar(lwd = 0.5)))

hm_150_0.05_bait <- grid.grabExpr(
    hm1b <- draw(hm1b_loose, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm / 1.05, height = h_ipmsHm / 2.2
)

@@

hm1b2 <- Heatmap(baitdata_500$mat, 
                 cluster_rows = FALSE, 
                 cluster_columns = FALSE, 
                 col = makeHeatmapCol(stringency = "high"), 
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.", 
                 na_col = binary_heatmap_colors["FALSE"],
                 column_title = paste(c("500 mM NaCl", rep(" ", 45)), collapse = ""),
                 row_title = "Transcription factors",
                 column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                 row_title_gp = gpar(fontsize = fl),
                 column_names_gp = gpar(fontsize = fs),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = FALSE, show_column_names = FALSE,
                 use_raster = FALSE, show_heatmap_legend = TRUE,
                 left_annotation = makeComplexAndDBDAnnotation(
                     baitdata_500$mat, 
                     complexes[c("MBF transcription complex", 
                                 "CCAAT-binding factor complex", "Atf1-Pcr1")], 
                     dbd = dbd, idmap = idmap),
                 top_annotation = makeTFIntAnnotation(baitdata_500), 
                 width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                 heatmap_height = unit(h_ipmsHm / 2.2, "mm"), # whole heatmap height
                 heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

hm_500_bait <- grid.grabExpr(
    hm1b2 <- draw(hm1b2, merge_legend = TRUE,
                  heatmap_legend_side = "right",
                  annotation_legend_side = "right"),
    width = w_ipmsHm / 1.05, height = h_ipmsHm / 2.2
)

@@

## Subset 2
lowhighsub2 <- lowhigh |> 
    dplyr::filter(splitvar %in% c("Atf1", "Pcr1", "Moc3", 
                                  "Dal2", "Ntu1", "Ntu2")) |>
    dplyr::mutate(splitvar = factor(splitvar, levels = c("Atf1", "Pcr1", "Moc3", 
                                                         "Dal2", "Ntu1", "Ntu2"))) |>
    dplyr::mutate(significant = (adjp_high < adjp150vs500 & logfc_high > logfc150vs500))

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        plot_grid(gg_retain1, NULL, hm_150_saga_nua4, nrow = 1, rel_widths = c(1, 0.05, 0.75)),
        gg_retain2,
        hm_150_bait, hm_500_bait,
        rel_heights = c(7, 4),
        labels = c("A", "B", "C", "D")
    ),
    cowplot::plot_grid(
        NULL,
        legend_bait_1, 
        legend_bait_2,
        NULL,
        nrow = 1,
        rel_widths = c(1, 2, 2, 1)
    ),
    nrow = 2,
    rel_heights = c(12, 1)
)
```

>>>>

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, 
                    idmap = idmap),
                top_annotation = makeTFIntAnnotation(baitdata_150), 
                bottom_annotation = makeColLabels(baitdata_150_loose$mat, 
                                                  c("Ntu1_plate", "Ntu2_plate", 
                                                    "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 1.7, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

set.seed(42L)
hm_150_bait <- grid.grabExpr(
    hm1b <- draw(hm1b, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm / 1.05, height = h_ipmsHm / 1.7
)

@@

dbd_colors <- c(`KilA-N` = main_colors[5], 
                `Zn(II)2Cys6` = main_colors[4],
                bZIP = main_colors[3], 
                bHLH_SF = main_colors[2],
                `Other (combined)` = bg_color)
lgd_dbd <- Legend(labels = names(dbd_colors), 
                  legend_gp = gpar(fill = dbd_colors), 
                  title = "DBD family", nrow = 2)

@@

hm1b_loose <- Heatmap(baitdata_150_loose$mat, 
                      cluster_rows = FALSE, 
                      cluster_columns = FALSE, 
                      col = makeHeatmapCol(stringency = "low"), 
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.", 
                      na_col = binary_heatmap_colors["FALSE"],
                      column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                      row_title = "Transcription factors",
                      column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                      row_title_gp = gpar(fontsize = fl),
                      column_names_gp = gpar(fontsize = fs),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = FALSE, show_column_names = FALSE,
                      use_raster = FALSE, show_heatmap_legend = TRUE, 
                      left_annotation = makeComplexAndDBDAnnotation(
                          baitdata_150_loose$mat, 
                          complexes[c("MBF transcription complex", 
                                      "CCAAT-binding factor complex",
                                      "Atf1-Pcr1")],
                          dbd = dbd, 
                          idmap = idmap),
                      top_annotation = makeTFIntAnnotation(baitdata_150_loose), 
                      bottom_annotation = makeColLabels(baitdata_150_loose$mat, 
                                                  c("Ntu1_plate", "Ntu2_plate", 
                                                    "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                      heatmap_height = unit(h_ipmsHm / 1.7, "mm"), 
                      heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                                  border = "gray10",
                                                  border_gp = gpar(lwd = 0.5)))

hm_150_0.05_bait <- grid.grabExpr(
    hm1b <- draw(hm1b_loose, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm / 1.05, height = h_ipmsHm / 1.7
)

@@

hm1b2 <- Heatmap(baitdata_500$mat, 
                 cluster_rows = FALSE, 
                 cluster_columns = FALSE, 
                 col = makeHeatmapCol(stringency = "high"), 
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.", 
                 na_col = binary_heatmap_colors["FALSE"],
                 column_title = paste(c("500 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                 row_title = "Transcription factors",
                 column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                 row_title_gp = gpar(fontsize = fl),
                 column_names_gp = gpar(fontsize = fs),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = FALSE, show_column_names = FALSE,
                 use_raster = FALSE, show_heatmap_legend = TRUE,
                 left_annotation = makeComplexAndDBDAnnotation(
                     baitdata_500$mat, 
                     complexes[c("MBF transcription complex", 
                                 "CCAAT-binding factor complex", "Atf1-Pcr1")], 
                     dbd = dbd, idmap = idmap),
                 top_annotation = makeTFIntAnnotation(baitdata_500), 
                 bottom_annotation = makeColLabels(baitdata_500$mat, 
                                                  c("Ntu1_plate", "Ntu2_plate",
                                                    "Esc1_plate", "SPAC3F10.12c_plate"), fl),
                 width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                 heatmap_height = unit(h_ipmsHm / 1.7, "mm"), # whole heatmap height
                 heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

hm_500_bait <- grid.grabExpr(
    hm1b2 <- draw(hm1b2, merge_legend = TRUE,
                  heatmap_legend_side = "right",
                  annotation_legend_side = "right"),
    width = w_ipmsHm / 1.05, height = h_ipmsHm / 1.7
)

@@

## Subset 2
lowhighsub2 <- lowhigh |> 
    dplyr::filter(splitvar %in% c("Atf1", "Pcr1", "Moc3", 
                                  "Dal2", "Ntu1", "Ntu2")) |>
    dplyr::mutate(splitvar = factor(splitvar, levels = c("Ntu1", "Ntu2", 
                                                         "Atf1", "Pcr1", 
                                                         "Moc3", "Dal2"))) |>
    dplyr::mutate(significant = (adjp_high < adjp150vs500 & logfc_high > logfc150vs500))

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        hm_150_bait, hm_500_bait,
        gg_retain2,
        plot_grid(gg_retain1, NULL, hm_150_saga_nua4, nrow = 1, rel_widths = c(1, 0.05, 0.75)),
        rel_heights = c(4, 7),
        labels = c("A", "B", "C", "D")
    ),
    cowplot::plot_grid(
        NULL,
        legend_bait_1, 
        legend_bait_2,
        NULL,
        nrow = 1,
        rel_widths = c(1, 2, 2, 1)
    ),
    nrow = 2,
    rel_heights = c(12, 1)
)
```
